% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Rizhen Zhang}
% \address used twice to have two lines of address
\addressa{Dorm 11-211, Nanjing University, Nanjing, China, 210093}
\addressb{+(86)15298388031 $\diamond$ email: sheimi.zhang@gmail.com}
\addressc{http://blog.sheimi.me $\diamond$ http://blog.sheimi.me/projects}

 
\begin{resume}
 
\section{Education}
{\sl Bachelor of Engineering,} Software Engineering\\
  Software Institute, Nanjing University, expected June 2013\\
  GPA: 4.48\\
  Rank: 3 / 185

\section{Awords}
National Scholarship, 2009 - 2010 \\
Samsung Scholarship, 2010 - 2011

\section{Internship \& Employment}
{\sl Product Developer (Intern)} \hfill July 2012 - Sep. 2012\\
    Analytics Platform \& Delivery Department, eBay COE China
    \begin{itemize} \itemsep -2pt
    \item Responsible for the web application of a project, "Global View"
    \item Redesigned the web interface of "Global View"
    \end{itemize}

\section{Research Experience}
{\sl Media Cloud} \hfill May 2011 - Mar. 2012\\
This is a national innovation project. We are trying to find ways to apply
distributed computing and storage on multimedia processing for research purpose.

\section{Projects}
{\sl MyLex} \hfill Oct. 2012 
    \begin{itemize} \itemsep -2pt
    \item Homework of "Principle of Compilers", a tiny lexical analyzer
          generator
    \item A personal project
    \item Implemented in C++
    \end{itemize}

{\sl Danger KO} \hfill Sep. 2010 - Nov. 2010 
    \begin{itemize} \itemsep -2pt
    \item A danger inform app on android
    \item Prized for excellence in an Android App Contest held by Google Inc
    \item It is a team project and I'm responsible for the backend of this
          application
    \end{itemize}

{\sl Online Shop} \hfill Mar. 20112 
    \begin{itemize} \itemsep -2pt
    \item Web homework, a e-commerce system.
    \item A personal project.
    \item Implemented in Python, based on Flask Framwork
    \end{itemize}
 
\section{Computer Skills}
{\sl Programming Languages: } Python, C, C++, Java, Javascript ...\\
{\sl Operating Systems:} Linux, Mac OS\\
{\sl Tools \& Softwares:} Vim, Git, Eclipse ...\\
{\sl Others:} Familiar with web development and have some knowledge about
              hadoop, pig, hbase and zookeeper
 
\section{Community Service}  \hfill July 2011\\
  Organized a team to help people solve problem about computer or mobile
  phone.\\
  Provided service like reinstalling operating system, rooting android mobile
  and killing computer virus .

\end{resume}
\end{document}







